### 2019-07-26 appendix/appendix-institutional-design-climate-policy.Rmd
revision v2.0

---
title: |
       | Supplementary Materials for "Institutional Design and Elite Support for Climate Policies: Evidence from Latin American Countries"
author: 
- "Danilo Freire[^freire]"
- "Umberto Mignozzetti[^mignozzetti]"
- "David Skarbek[^skarbek]"
date: July 25, 2019
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

@@

```{r demogGraph, echo=FALSE, fig.align='center', fig.height=3.5, message=FALSE,warning=F}
library(plm); library(tidyverse)
library(haven); library(clusterSEs)
library(stargazer); library(cjoint)
library(sp); library(cregg)
library(kableExtra)
load('freire-mignozzetti-skarbek.RData')

@@

```{r attributes, echo=FALSE, fig.align='center', fig.height=4}
aux <- cj %>%
  select(Response.ID, `Who makes the rules?`, `How are conflicts resolved?`, `What punishments do they use?`,`How are repeated violations punished?`, `How are costs distributed?`,`How often will the agreement be renegotiated?`) %>%
  unique()

@@

```{r, fig.width = 7, fig.height = 8}
## Main model
rm(cj)
load('freire-mignozzetti-skarbek.RData')

@@

**Random Assignment:** We programmed the experiment using a Python application provided by @strezhnev2013conjoint. We translated the original survey questions (as shown in the text) into Portuguese and Spanish, and then embedded the PHP file with the randomization parameters in a Qualtrics survey. The PHP code we used to randomize the values of the attributes is available at the project's GitHub repository: <http://github.com/danilofreire/climate-governance>.

@@

\noindent \textbf{Questionnaire:} For the English translation of the entire survey instrument, with both the telephone and the online components, see the attachment below.

@@

```{r, fig.width = 7, fig.height = 8}
barplot(100*table(cj$task)/max(table(cj$task)), xlab = 'Conjoint task', ylab = 'Percentage completed')
```

>>>>

---
title: |
       | Supplementary Materials for "Institutional Design and Elite Support for Climate Policies: Evidence from Latin American Countries"
author: 
- "Danilo Freire[^freire]"
- "Umberto Mignozzetti[^mignozzetti]"
- "David Skarbek[^skarbek]"
date: July 26, 2019
fontfamily: libertine
fontawesome: yes
fontsize: 12pt
monospace-url: yes
spacing: double
papersize: a4paper
bibliography: references.bib
biblio-style: apalike
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: true
    keep_tex: no
    template: template.latex
---

@@

```{r demogGraph, fig.align='center', fig.height=3.5, message=FALSE,warning=F}
library(plm); library(tidyverse)
library(haven); library(clusterSEs)
library(stargazer); library(cjoint)
library(sp); library(cregg)
library(kableExtra)
load('data.RData')

@@

```{r attributes, fig.align='center', fig.height=4}
aux <- cj %>%
  select(Response.ID, `Who makes the rules?`, `How are conflicts resolved?`, `What punishments do they use?`,`How are repeated violations punished?`, `How are costs distributed?`,`How often will the agreement be renegotiated?`) %>%
  unique()

@@

```{r, fig.width = 7, fig.height = 8}
## Main model
rm(cj)
load('data.RData')

@@

**Random Assignment:** We programmed the experiment using a Python application provided by @strezhnev2013conjoint. We translated the original survey questions (as shown in the text) into Portuguese and Spanish, and then embedded the PHP file with the randomization parameters in a Qualtrics survey. The PHP code we used to randomize the values of the attributes is available at the project's GitHub repository: <https://github.com/danilofreire/climate-governance>.

@@

@@

```{r, fig.width = 7, fig.height = 5, tidy=FALSE}
barplot(100*table(cj$task)/max(table(cj$task)),
        xlab = 'Conjoint task',
        ylab = 'Percentage completed')
```

### 2019-07-26 manuscript/institutional-design-climate-policy.tex
revision v2.0

\title{Institutional Design and Elite Support for Climate Policies: Evidence from Latin American Countries\thanks{We thank Nigel Ashford, F\'{a}bio Barros, Frans Berkhout, Daniel D'Amico, Guilherme Fasolin, Manoel Galdino, Malte Hendricks, Stephen Herzog, Christian H\"{u}bner, Karina Marzano, Davi Moreira, Emily Skarbek, Paula Vedovelli, and the participants at the FGV IR Seminar for their valuable comments. Special thanks to Natalia Liberato, Lucas Mingardi, Ingrid Oliveira, Catarina Roman, Leticia Santana, and Larissa Santos for their excellent research assistance. This research received IRB approval from Brown University (Protocol 2195/2018) and Funda\c{c}\~{a}o Getulio Vargas (Protocol 83/2018). We acknowledge financial support from the Konrad Adenauer Stiftung Latin American Regional Programme for Energy Security and Climate (EKLA-KAS) and declare there are no conflicts of interest. The data, code, and additional materials required to replicate all analyses in this article are available at \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}}.}
}

\author{Danilo Freire\thanks{Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, \href{mailto:danilo_freire@brown.edu}{\texttt{danilo\_freire@brown.edu}}, \href{http://danilofreire.github.io}{\texttt{http://danilofreire.github.io}}, \href{http://twitter.com/danilofreire}{\texttt{http://twitter.com/danilofreire}}, Voice: +1 (401) 584-2494. Corresponding author.}
\and Umberto Mignozzetti\thanks{School of International Relations, Funda\c{c}\~{a}o Getulio Vargas, S\~{a}o Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA, \href{mailto:umberto.mignozzetti@fgv.br}{\texttt{umberto.mignozzetti@fgv.br}}, \href{http://umbertomig.com}{\texttt{http://umbertomig.com}}, \href{http://twitter.com/umbertomig}{\texttt{http://twitter.com/umbertomig}}.}
\and David Skarbek\thanks{The Department of Political Science and the Political Theory Project, Brown University, Providence, RI, USA, \href{mailto:david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}}, \href{http://davidskarbek.com}{\texttt{http://davidskarbek.com}}, \href{http://twitter.com/davidskarbek}{\texttt{http://twitter.com/davidskarbek}}.}
}

@@

\noindent 
\textbf{Word count:} 3908
\end{abstract}

@@

These concerns have motivated a growing debate about which institutional characteristics lead to successful climate agreements \citep[e.g.,][]{aklin2013understanding, bechtel2013mass, bechtel2017interests, keohane2011regime, ostrom2014polycentric}. Climate treaties are incomplete contracts, in which members purposefully design flexible provisions that take domestic circumstances into account \citep[607]{brauninger2000making}. For instance, the Paris Agreement relies on Nationally Determined Contributions (NDCs), a set of greenhouse gas reduction targets each member state voluntarily pledges to achieve \citep{winning2019nationally}. This decentralization increases the importance of national stakeholders in climate negotiations, and studies have shown that the behavior of elite groups, like advocacy coalitions and political parties, largely explain countries' climate policy performance \citep{jahn2016politics, karapin2012explaining}.

Elites engage in different forms of `societal steering' to achieve policy goals, such as information sharing or rule setting \citep{andonova2009transnational, bulkeley2014transnational}. For example, non-governmental organizations have played a major role in the fossil fuel divestment movement by highlighting the urgency of the topic in developed countries \citep{ayling2017non}. In contrast, Brazil's rural caucus, an informal coalition of landholders and mining industrialists, have successfully lobbied for legislation that undermines previous carbon emission policies \citep{rochedo2018threat, simionatto2012dominantes}. Therefore, understanding the preferences of elite groups provides policy-makers with key information for designing effective, politically viable climate agreements.

Although research on public opinion about climate change has increased significantly in the last years \citep[e.g.,][]{aklin2013understanding, bechtel2013mass, bechtel2017interests, mildenberger2017beliefs}, elite preferences are not well documented in the literature. This is a significant omission considering their importance as lobbyists or veto players in domestic climate politics. Elites in developing countries are specially understudied, despite the fact that emerging economies account for 63\% of the world's carbon emissions \citep{busch2015developing}. It is unclear which climate strategies face lower internal resistance from these groups, or whether their environmental preferences are fundamentally different from those of their developed countries counterparts \citep[28]{aklin2013understanding}.

@@

\begin{table}[H]
\small
\begin{center}
\caption{\textbf{Attributes and values for climate change mitigation conjoint experiments}}
\label{tab:categories} 
\begin{tabular}{l !{\vrule width 1pt}p{9cm}}
\Xhline{2\arrayrulewidth}
\textbf{Attribute} & \multicolumn{1}{c}{\textbf{Values}} \\
\Xhline{2\arrayrulewidth} 
Who makes the rules? & International organizations; federal government; local government; local community members; non-governmental organizations \\
& \\
Conflict resolution mechanism & United Nations; government bureaucracy; local courts; private arbitration; informal norms \\
& \\
Punishment & Imprisonment; fines; blacklist; none \\
& \\
Punishment for repeated violations & More penalty; same; less penalty \\
& \\
Agreement costs & Rich countries pay more than poor countries; proportional to history of emissions; proportional to current emissions; only rich countries pay \\
& \\
Renegotiation & Never; fifty years; twenty years; five years; one year \\
\Xhline{2\arrayrulewidth} 
\end{tabular}
\end{center}
\end{table}

>>>>

\title{Institutional Design and Elite Support for Climate Policies: Evidence from Latin American Countries\thanks{We thank Nigel Ashford, F\'{a}bio Barros, Frans Berkhout, Daniel D'Amico, Guilherme Fasolin, Manoel Galdino, Malte Hendricks, Stephen Herzog, Christian H\"{u}bner, Karina Marzano, Davi Moreira, Emily Skarbek, Paula Vedovelli, and the participants at the FGV IR Seminar for their valuable comments. Special thanks to Natalia Liberato, Lucas Mingardi, Ingrid Oliveira, Catarina Roman, Leticia Santana, and Larissa Santos for their excellent research assistance. This research received IRB approval from Brown University (Protocol 2195/2018) and Funda\c{c}\~{a}o Getulio Vargas (Protocol 83/2018). We acknowledge financial support from the Konrad Adenauer Stiftung Latin American Regional Programme for Energy Security and Climate (EKLA-KAS) and declare there are no conflicts of interest. The data, code, and additional materials required to replicate all analyses in this article are available at \href{http://github.com/danilofreire/climate-governance}{\texttt{http://github.com/danilofreire/climate-governance}}.}}

\author{Danilo Freire\thanks{Postdoctoral Research Associate, The Political Theory Project, Brown University, Providence, RI 02912, USA, \href{mailto:danilo_freire@brown.edu}{\texttt{danilo\_freire@brown.edu}}, \href{http://danilofreire.github.io}{\texttt{http://danilofreire.github.io}}, \href{http://twitter.com/danilofreire}{\texttt{http://twitter.com/danilofreire}}, Voice: +1 (401) 584-2494. Corresponding author.}
\and Umberto Mignozzetti\thanks{School of International Relations, Funda\c{c}\~{a}o Getulio Vargas, S\~{a}o Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA, \href{mailto:umberto.mignozzetti@fgv.br}{\texttt{umberto.mignozzetti@fgv.br}}, \href{http://umbertomig.com}{\texttt{http://umbertomig.com}}, \href{http://twitter.com/umbertomig}{\texttt{http://twitter.com/umbertomig}}.}
\and David Skarbek\thanks{The Department of Political Science and the Political Theory Project, Brown University, Providence, RI, USA, \href{mailto:david_skarbek@brown.edu}{\texttt{david\_skarbek@brown.edu}}, \href{http://davidskarbek.com}{\texttt{http://davidskarbek.com}}, \href{http://twitter.com/davidskarbek}{\texttt{http://twitter.com/davidskarbek}}.}}

@@

\noindent 
\textbf{Word count:} 3839
\end{abstract}

@@

These concerns have motivated a growing debate about which institutional characteristics lead to successful climate agreements \citep[e.g.,][]{bechtel2013mass, bechtel2017interests, keohane2011regime, mitchell2006problem, ostrom2014polycentric}. Climate treaties are incomplete contracts, in which members purposefully design flexible provisions that take domestic circumstances into account \citep[607]{brauninger2000making}. For instance, the Paris Agreement relies on Nationally Determined Contributions (NDCs), a set of greenhouse gas reduction targets each member state voluntarily pledges to achieve \citep{winning2019nationally}. This decentralization increases the importance of national stakeholders in climate negotiations, and studies have shown that the behavior of elite groups -- specially that of advocacy coalitions and political networks -- largely explain countries' climate policy performance \citep{jahn2016politics, karapin2012explaining}. Elites can advance or constrain climate agreements using `societal steering' strategies such as capacity building and rule setting, thus acting as \textit{de facto} veto players in local environmental policies \citep{andonova2009transnational, bulkeley2014transnational}.

Although research on public opinion and climate agreements has increased significantly in the last years \citep[e.g.,][]{aklin2013understanding, bechtel2013mass, bechtel2017interests, mildenberger2017beliefs}, elite preferences are not well documented in the literature. This is a significant omission considering that recent work has stressed the impact of elite coalitions in areas such as global finance and international banking regulation \citep[e.g,][]{chalmers2017banks, pagliari2014leveraged}. Elites in developing countries are specially understudied, despite the fact that emerging economies account for 63\% of the world's carbon emissions \citep{busch2015developing}. It is unclear which climate strategies face lower internal resistance from these groups, or whether their environmental preferences are fundamentally different from those of their developed countries counterparts \citep[28]{aklin2013understanding}.

@@

\begin{table}[H]
\begin{center}
\caption{\textbf{Attributes and values for climate change mitigation conjoint experiments}}
\label{tab:categories} 
\begin{tabular}{l !{\vrule width 1pt}p{9cm}}
\Xhline{2\arrayrulewidth}
\textbf{Attribute} & \multicolumn{1}{c}{\textbf{Values}} \\
\Xhline{2\arrayrulewidth} 
Who makes the rules? & International organizations; federal government; local government; local community members; non-governmental organizations \\
& \\
Conflict resolution mechanism & United Nations; government bureaucracy; local courts; private arbitration; informal norms \\
& \\
Punishment & Imprisonment; fines; blacklist; none \\
& \\
Punishment for repeated violations & More penalty; same; less penalty \\
& \\
Agreement costs & Rich countries pay more than poor countries; proportional to history of emissions; proportional to current emissions; only rich countries pay \\
& \\
Renegotiation & Never; fifty years; twenty years; five years; one year \\
\Xhline{2\arrayrulewidth} 
\end{tabular}
\end{center}
\end{table}
